Psych 254 Replication Project Analysis

### 2016-06-24 analysis.Rmd
Analysis update no plyr

```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(googlesheets)
library(readr)
library(tidyr)
```

@@

# Run all respective R code - need loop because project_keys same variable name
rm("project_info") # In case var is saved
for(project_key in temp_project_keys) { # change from temp - test; project_key <- "smraposo"
  fp <- paste0("project_analyses/",project_key,".R")
  source(fp)
  #tryCatch(source(fp), error=function(e) {errors <- c(errors,paste0(project_key," has an error in .R file"),print(fp))}) 
  if(exists("project_info")) { # If has project_info dataframe
    all_project_info <- rbind.fill(all_project_info,project_info) # add to all data
    rm("project_info") # In case other file does not same
  } else {
    errors <- c(errors,paste0(project_key," is missing project_info"))
  }
}

>>>>

```{r}
library(dplyr)
library(ggplot2)
library(googlesheets)
library(readr)
library(tidyr)
```

@@

# Run all respective R code - need loop because project_keys same variable name
rm("project_info") # In case var is saved
for(project_key in temp_project_keys) { # change from temp - test; project_key <- "smraposo"
  fp <- paste0("project_analyses/",project_key,".R")
  #source(fp)
  tryCatch(source(fp), error=function(e) {errors <- c(errors,paste0(project_key," has an error in .R file"),print(fp))}) 
  if(exists("project_info")) { # If has project_info dataframe
    all_project_info <- bind_rows(all_project_info,project_info) # add to all data
    rm("project_info") # In case other file does not same
  } else {
    errors <- c(errors,paste0(project_key," is missing project_info"))
  }
}
